Species-specific effects of the Urban Heat Island on tree growth across Berlin

### 2020-03-05 analysis/paper/paper.Rmd
updated figures
fixing onedrive issues

---
title: "Exploratory overview of Berlin city trees"
author:
  - Alexander Hurley:
      email: hurley@gfz-potsdam.de
      institute: [GFZ]
      correspondence: true
  - Ingo Heinrich:
      email: heinrich@gfz-potsdam.de
      institute: [GFZ]
      correspondence: false
institute:
  - GFZ: Geoforschungszentrum Potsdam
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes

bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Quick overview of publicly available tree records.
keywords: |
  Uferbaeume; Anlagenbaeume; Strassenhighlights
highlights: |
  We will see. 
---

@@

library(drake)
library(ggplot2)
```

@@

```{r fig-tree-overview-map, fig.cap="A plot of random numbers",fig.width = 15, fig.height = 8, out.width="100%"}
readd(plot_overview_map)
# plot_overview_map

@@

```{r fig-tree-count-map, fig.cap="A plot of random numbers",fig.width = 12, fig.height = 12, out.width="100%"}
readd(plot_count_map)
# plot_count_map

>>>>

---
title: "Species-specific effects of the Urban Heat Island on tree growth across Berlin"
author:
  - Alexander Hurley:
      email: hurley@gfz-potsdam.de
      institute: [GFZ]
      correspondence: true
  - Ingo Heinrich:
      email: heinrich@gfz-potsdam.de
      institute: [GFZ]
      correspondence: false
institute:
  - GFZ: Geoforschungszentrum Potsdam
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      toc: yes
    bookdown::pdf_document2:
      fig_caption: yes
      toc: yes

bibliography: uhi_references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  **This document serves as a brief overview and outline** .
keywords: |
  Uferbaeume; Anlagenbaeume; Strassenbaeume; 
highlights: |
  We will see. 
---

@@

library(drake)
library(ggplot2)
library(patchwork)
```

@@

```{r fig-tree-overview-map, fig.cap="A plot of random numbers",fig.width = 15, fig.height = 8, out.width="100%", include=TRUE, eval=TRUE}

# loadd(full_data_set_clean)
# loadd(plot_overview_map)
# print(class(full_data_set_clean))

# knitr::include_graphics(drake::file_in("./analysis/figures/map_01_overview.png"))

loadd(plot_overview_map)
knitr::include_graphics(file.path(here::here(), "analysis", "figures", "map_01_overview.png"))
# knitr::include_graphics("../figures/map_01_overview.png")
# print(dir(path = "./analysis/figures"  ))
# readd(plot_overview_map) + 
#      +
#     labs(caption = NULL)

# plot_overview_map

@@

```{r fig-uhi, fig.cap="A plot of random numbers",fig.width = 15, fig.height = 8, out.width="100%", include=TRUE, eval=TRUE}

loadd(plot_uhi_map)
knitr::include_graphics(file.path(here::here(),
                                                 "analysis", 
                                                 "figures", 
                                                 "map_03_uhi.png"))
# knitr::include_graphics(drake::file_in(file.path(here::here(),
#                                                  "analysis", 
#                                                  "figures", 
#                                                  "map_03_uhi.png")))

```{r fig-tree-count-map, fig.cap="A plot of random numbers",fig.width = 12, fig.height = 14, out.width="100%"}

loadd(plot_count_map)
knitr::include_graphics(file.path(here::here(), "analysis", "figures", "map_02_tree_sums_standardized.png"))

# readd(plot_count_map) + 
#   labs(caption = NULL) +
#   theme(legend.position = c(0.65, 0.1),
#         legend.key.width = unit(3, units = "cm")) +
#   guides(color = guide_colorbar(title.position = "top"))

# plot_count_map

```{r fig-count-bars, fig.cap="A plot of random numbers",fig.width = 6, fig.height = 6, out.width="50%", include = FALSE, eval = FALSE}
loadd(plot_tree_sums_bar)
knitr::include_graphics(file.path(here::here(), "analysis", "figures", "plot_01_tree_sums_bar.png"))

```{r fig-density, fig.cap="A plot of random numbers",fig.width = 12, fig.height = 12, out.width="100%"}
loadd(plot_density)
knitr::include_graphics(file.path(here::here(), "analysis", "figures", "plot_02_genus_UHI_dens.png"))

```{r fig-lmestat, fig.cap="A plot of random numbers",fig.width = 20, fig.height = 12, out.width="100%"}
loadd(plot_LME_age)
knitr::include_graphics(file.path(here::here(), "analysis", "figures", "plot_03_ranef_species_dbh_uhi.png"))
